Restrictive Clearance Comparison

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Finishing the preliminary implementation of restrictive/non-restrictive clearance models

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_flat", "model_1comp",
                       "model_1comp_rest", "model_1comp_nonrest"))
new_pk <- do_data_info(new_pk)

@@

new_pk$prefit$par_DF %>% View()

@@

pl <- plot(new_pk, use_scale_conc = TRUE, method = "L-BFGS-B", n_interp = 10)

>>>>

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
                       "model_1comp_rest", "model_1comp_nonrest",
                       "model_2comp_rest", "model_2comp_nonrest"))
new_pk <- do_data_info(new_pk)

@@

new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "kelim") %>%
  View()

@@

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           model = "model_2comp_nonrest",
           n_interp = 10)

pl2comp %>%
  filter(Chemical %in% "DTXSID0021383") %>% pull(final_plot) %>% .[[1]]
```
